\thetitle

### 2020-11-21 writing/landscape.tex
Fix typo

\smallskip
\noindent
{\bf Note.} As the common basis for the three semantics, we choose 
Typed Racket's migratory typing. In contrast to the initial formulation of
gradual typing~\cite{st-sfp-2006}, migratory typing does not provide
support for type \texttt{Dyn}, components are either untyped or fully
typed and the gradual type system does not affect the compilation of
untyped components. Despite, these differences, Typed Racekt is the most
mature system for sound mix-typed code
and recent theoretical work has established that
its migratory typing offers a setting for comparing different approaches to gradual
typing~\cite{gf-icfp-2018,gfd-oopsla-2019}.

>>>>

\smallskip
\noindent
{\bf Note.} As the common basis for the three semantics, we choose 
Typed Racket's migratory typing. In contrast to the initial formulation of
gradual typing~\cite{st-sfp-2006}, migratory typing does not provide
support for type \texttt{Dyn}, components are either untyped or fully
typed and the gradual type system does not affect the compilation of
untyped components. Despite, these differences, Typed Racket is the most
mature system for sound mix-typed code
and recent theoretical work has established that
its migratory typing offers a setting for comparing different approaches to gradual
typing~\cite{gf-icfp-2018,gfd-oopsla-2019}.
